SHARP - II: Revealing a bias in observational measurements of dark matter substructure with gravitational lens flux ratios

### 2015-11-12 papers/B1555_EdgeOn/B1555_letter.tex
update reference link in text

\begin{table}
\centering
\caption{Best-fit model parameters and uncertainties for our two-component SIE + exponential disc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99} and so is not shown here). The positions are measured in arcsec, relative to the radio position of image A. The ellipticity is defined as $e=1-q$ and the position angles are measured in degrees east of north. The Einstein radius $b$ and disc scale radius are measured in arcsec.}
\begin{tabular}{ccc}
\hline 
Parameter    & SIE Component & ExpDisc Component  \\
%   & (SIE) & (ExpDisc)\\
\hline
$\Delta$RA	& $-0.182 \pm 0.005$		& $-0.147 \pm 0.005$\\
$\Delta$Dec	& $-0.199 \pm 0.005$		& $-0.206 \pm 0.006$ \\
$b$ 			& $0.21 \pm 0.01$  		& $0.11 \pm 0.01$  \\
$e$	  		& $0.31 \pm 0.01$			& $0.87 \pm 0.01$ \\
$\theta$ 		& $3.0 \pm 0.6$			& $7.0 \pm 0.7$	 \\
$R_s$			& ...  						& $0.28 \pm 0.01$	 \\
\hline
\label{tab:model}
\end{tabular}
\end{table}

@@

{\bf Here, we find evidence for an edge-on disc in the flux-ratio
anomalous gravitational lens B1555+375 that can also account for
the required perturbation in the mass model. Such high-order deviations from a smooth mass distribution have already been suggested previously (Evans \& Witt 2003; Congdon \& Keeton 2005), but this is the first time that an observed disc has been explicitly modelled to account for a flux-ratio anomaly. However, it is important to realise that by including observationally-motivated perturbations to a `smooth' mass distribution, like luminous dwarf companions or edge-on discs, in the mass models,
we are still limited in our interpretation since we must assume that
the anomalies are due exclusively to these additional components.
For B1555+375, it may be possible to independently constrain the
mass of the disc through kinematic measurements (most likely from
mm-wavelength resolved emission line observations), which would
test whether the disc makes a sufficient contribution to the mass
model (e.g. as in the case of B1933+503; Suyu et al. 2012). Also, as
we have shown here, B1555+375 shows evidence for an extended $\sim$ 100 mas gravitational arc at radio wavelengths that crosses the
edge-on disc. Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the disc is sufficient to cause the anomaly.}

{\bf Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with
the limited information provided by the position of compact lensed
images, can lead to a misinterpretation of the origin of flux-ratio anomalies. Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, then, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account (e.g., Xu et al.~2015). This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can be measured using narrow lines (e.g., Nierenberg et al.~2014). Near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components. Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyways; Evans \& Witt 2003), indicating that these systems are still useful for probing the dark matter substructure mass function.}

>>>>

\begin{table}
\centering
\caption{Best-fit model parameters and uncertainties for our two-component SIE + exponential disc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99} and so is not shown here). The positions are measured in arcsec, relative to the radio position of image A. The ellipticity is defined as $e=1-q$ and the position angles are measured in degrees east of north. The Einstein radius $b$ and disc scale radius are measured in arcsec.}
\begin{tabular}{ccc}
\hline 
Parameter    & SIE Component & ExpDisc Component  \\
%   & (SIE) & (ExpDisc)\\
\hline
$\Delta$RA	& $-0.182 \pm 0.005$		& $-0.147 \pm 0.005$\\
$\Delta$Dec	& $-0.199 \pm 0.005$		& $-0.206 \pm 0.006$ \\
$b$ 			& $0.21 \pm 0.01$  		& ...  \\
$\kappa_0$ & ... &$0.11 \pm 0.01$\\
$e$	  		& $0.31 \pm 0.01$			& $0.87 \pm 0.01$ \\
$\theta$ 		& $3.0 \pm 0.6$			& $7.0 \pm 0.7$	 \\
$R_s$			& ...  						& $0.28 \pm 0.01$	 \\
\hline
\label{tab:model}
\end{tabular}
\end{table}

@@

{\bf Here, we find evidence for an edge-on disc in the flux-ratio
anomalous gravitational lens B1555+375 that can also account for
the required perturbation in the mass model. Such high-order deviations from a smooth mass distribution have already been suggested previously \citep{evans03, congdon05}, but this is the first time that an observed disc has been explicitly modelled to account for a flux-ratio anomaly. However, it is important to realise that by including observationally-motivated perturbations to a `smooth' mass distribution, like luminous dwarf companions or edge-on discs, in the mass models,
we are still limited in our interpretation since we must assume that
the anomalies are due exclusively to these additional components.
For B1555+375, it may be possible to independently constrain the
mass of the disc through kinematic measurements (most likely from
mm-wavelength resolved emission line observations), which would
test whether the disc makes a sufficient contribution to the mass
model (e.g. as in the case of B1933+503; \citet{suyu12}). Also, as
we have shown here, B1555+375 shows evidence for an extended $\sim$ 100 mas gravitational arc at radio wavelengths that crosses the
edge-on disc. Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the disc is sufficient to cause the anomaly.}

\textbf{ Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies. Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, then, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account 
 (e.g., \citet{Xu15}). This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
  be measured using narrow lines (e.g., \citet{N14}). Near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components. Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyways; \citet{evans03}), indicating that these systems are still useful for probing the dark matter substructure mass function.}
